On the Construction of Isomorphic Interpreters

### 2012-02-17 iso-int/iso-int.tex
doing pi is difficult - for the wrong reasons

TODO : The real difficulty with this interpreter is to argue why it is
not full of undefined states. For instance, why the machines will
never reach stuck states such as {{<c1(+)c2, (), ..>}}.

The right way out of that is to make the type system of the abstract
machine rich enough that the structure of the abstract automatically
rules out this sort of thing.

>>>>

TODO : The real difficulty with this interpreter is to argue why it is
not full of undefined states. For instance, why the machines will
never reach stuck states such as {{<c1(+)c2, (), ..>}}.  The right way
out of that is to make the type system of the abstract machine rich
enough that the structure of the abstract automatically rules out this
sort of thing.

%subcode{bnf} include main
% Combinators, c(t1<->t2) = 
%             &|& c(t<->t) = iso 
%             &|& c(t1<->t2) = c(t1<->t3) (;) c(t3<->t2) 
%             &|& c(t1*t2<->t3*t4) = c(t1<->t3) (*) c(t2<->t4) 
%             &|& c(t1+t2<->t3+t4) = c(t1<->t3) (+) c(t2<->t4)
%
% Combinator Contexts, cc = [] | Fst cc c | Snd c cc 
%                  &|& LeftTimes cc c v | RightTimes c v cc 
%                  &|& LeftPlus cc c | RightPlus c cc 
%
% Type Indexed Values, v(t) =
%  &|& v(1) = () 
%  &|& v(t1*t2) = (v(t1), v(t2)) 
%  &|& v(t1+t2) = L v(t1) | R v(t2)
%
% Machine states = <c, v, cc> | {[c, v, cc]}
% Start state = <c, v, []> 
% Stop State = {[c, v, []]}

However this begs the question - does {{langRevT}} need all these GADT
types to reason about all these things? Something to think about. If
we do, then thereare two ways out

(1) add GADTs to {{langRevT}} and keep the structure of things
simple. They can always be added opaquely for any given types -- we
only need to add the proper fold/unflod morphisms for those types
(maybe).

(2) compile down to {{langRevT}} as it is. In this case, {{langRevT}}
is indeed a relatively less typed language than the source language
and will hence have to treat as stuck-states the non-type correct
machine states. We could apply omega to them and make them vanish --
for example. This is similar to the handling of the {{sub1}} in the
previous example.
